%-------------------------
% Resume in Latex (Heavily Expanded)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Jake's Resume} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:x@x.com}{\underline{jake@su.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jake}} $|$
    \href{https://github.com/...}{\underline{github.com/jake}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Southwestern University}{Georgetown, TX}
    {Bachelor of Arts in Computer Science, Minor in Business}{Aug. 2018 -- May 2021}
  \resumeSubheading
    {Blinn College}{Bryan, TX}
    {Associate's in Liberal Arts}{Aug. 2014 -- May 2018}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Undergraduate Research Assistant}{June 2020 -- Present}
    {Texas A\&M University}{College Station, TX}
    \resumeItemListStart
      \resumeItem{Developed RESTful services using FastAPI and PostgreSQL for data collection from LMS platforms}
      \resumeItem{Built visualization dashboards with React and D3.js to analyze team dynamics in software projects}
      \resumeItem{Applied NLP techniques to categorize student contributions in GitHub repositories}
    \resumeItemListEnd

  \resumeSubheading
    {Software Engineering Intern}{May 2020 -- Aug. 2020}
    {Dell Technologies}{Remote}
    \resumeItemListStart
      \resumeItem{Implemented telemetry microservices in Go and gRPC; improved request handling throughput by 32\%}
      \resumeItem{Automated container deployment pipelines with Helm and Azure DevOps}
      \resumeItem{Integrated Prometheus and Grafana dashboards for live performance analytics}
    \resumeItemListEnd

  \resumeSubheading
    {Machine Learning Intern}{Jan. 2020 -- Apr. 2020}
    {NASA – Goddard Space Flight Center}{Remote}
    \resumeItemListStart
      \resumeItem{Built convolutional neural network models in TensorFlow to classify satellite imagery for deforestation detection}
      \resumeItem{Optimized inference pipelines for onboard deployment on low-power Jetson Nano devices}
      \resumeItem{Wrote research summary presented at NASA Undergraduate Research Symposium}
    \resumeItemListEnd

  \resumeSubheading
    {Cybersecurity Research Assistant}{Sep. 2019 -- Jan. 2020}
    {Southwestern University}{Georgetown, TX}
    \resumeItemListStart
      \resumeItem{Analyzed 1M+ network packets using Python’s scapy and Wireshark for anomaly detection}
      \resumeItem{Developed intrusion-detection proof-of-concept with Flask dashboard visualization}
    \resumeItemListEnd


  \resumeSubheading
    {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
    {Southwestern University}{Georgetown, TX}
    \resumeItemListStart
      \resumeItem{Generated game dungeons using evolutionary algorithms inspired by \emph{The Legend of Zelda}}
      \resumeItem{Developed Java simulation engine and conducted human subject research to compare dungeon quality}
      \resumeItem{Presented work at the IEEE World Congress on Computational Intelligence}
    \resumeItemListEnd

  \resumeSubheading
    {Embedded Systems Teaching Assistant}{Jan. 2019 -- May 2019}
    {Southwestern University}{Georgetown, TX}
    \resumeItemListStart
      \resumeItem{Helped students debug embedded C code for Arduino and STM32 microcontrollers}
      \resumeItem{Authored automated test scripts to validate UART and I2C communication routines}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
      {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Developed interactive dashboards visualizing GitHub team metrics with D3.js and Plotly}
        \resumeItem{Implemented role-based access and OAuth with GitHub API integration}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{NeuroSketch} $|$ \emph{PyTorch, FastAPI, React, WebSockets}}{Jan. 2021 -- Apr. 2021}
      \resumeItemListStart
        \resumeItem{Developed AI-assisted sketching app generating art from textual prompts in real time}
        \resumeItem{Used GPU-based inference with TorchServe and WebSocket streaming}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{KubeChef} $|$ \emph{Go, Kubernetes, Docker, Helm, Prometheus}}{Sep. 2020 -- Dec. 2020}
      \resumeItemListStart
        \resumeItem{Created an operator to autoscale workloads based on queue latency and CPU utilization}
        \resumeItem{Implemented CI/CD via GitHub Actions and container image signing for integrity}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{EcoSort} $|$ \emph{TensorFlow, OpenCV, Raspberry Pi, Python}}{Feb. 2020 -- Apr. 2020}
      \resumeItemListStart
        \resumeItem{Built a real-time waste classifier achieving 91\% accuracy on a custom dataset of 10K images}
        \resumeItem{Controlled servo motors with GPIO for physical sorting}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Portfolio Tracker} $|$ \emph{Next.js, TypeScript, Firebase}}{Mar. 2021 -- May 2021}
      \resumeItemListStart
        \resumeItem{Developed a multi-user investment dashboard with real-time stock data via Polygon API}
        \resumeItem{Integrated authentication and Firestore data synchronization}
      \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Languages}{: Python, Java, C/C++, Go, TypeScript, Rust, SQL, Bash, HTML/CSS} \\
   \textbf{Frameworks}{: React, Next.js, Node.js, Flask, FastAPI, PyTorch, TensorFlow, Express.js, Spring Boot, OpenCV} \\
   \textbf{Cloud/DevOps}{: Docker, Kubernetes, Helm, GitHub Actions, AWS (EC2, S3, Lambda), GCP, Azure, Terraform, Prometheus, Grafana} \\
   \textbf{Databases}{: PostgreSQL, MongoDB, Redis, Firebase, SQLite, MySQL, Neo4j} \\
   \textbf{Tools}{: Git, VS Code, IntelliJ, PyCharm, JIRA, Wireshark, Postman, Figma, PowerShell, MATLAB} \\
   \textbf{Specialties}{: Full-Stack Development, Cloud Infrastructure, AI/ML, Computer Vision, Data Engineering, Systems Programming, Cybersecurity, Embedded Systems}
  }}
\end{itemize}

\end{document}
